\addcontentsline{toc}{chapter}{Authorship statement}
\begin{center}
\textbf{\large Co-authorship statement}
\end{center}


Co-authorship statements are described below for each chapter following the CRediT classification.

\paragraph{Chapter 1}
\textbf{MDu}: Writing – original draft.

\paragraph{Chapter 2}
\textbf{MDu}: Conceptualisation, Methodology, Software, Formal Analysis, Visualisation, Writing – original draft. \textbf{GP}: Conceptualisation, Supervision, Writing – review \& editing. \textbf{SLB}: Investigation, Writing – review \& editing. \textbf{MDa}: Conceptualisation, Investigation, Writing – review \& editing. \textbf{SFP}: Investigation, Writing – review \& editing. \textbf{LB}: Software, Visualisation. \textbf{LC}: Funding Acquisition, Resources. \textbf{MG}: Conceptualisation, Supervision, Writing – review \& editing.

\paragraph{Chapter 3}
\textbf{MDu}: Conceptualization, Investigation, Methodology, Software, Formal analysis, Visualisation, Funding Acquisition, Writing – original draft.
\textbf{CMY}: Conceptualization, Investigation, Methodology, Software, Formal analysis, Visualisation, Funding Acquisition, Writing – original draft. \textbf{GP}: Conceptualization, Methodology, Supervision, Writing – Review \& editing. \textbf{SFP}: Investigation, Writing – Review \& editing. \textbf{MDa}: Investigation, Funding Acquisition, Writing – Review \& editing. \textbf{KL}: Conceptualization, Supervision, Writing – Review \& editing. \textbf{TJL}: Investigation, Visualization, Writing – Review \& editing. \textbf{SF}: Methodology, Resources, Supervision, Writing – Review \& editing. \textbf{AB}: Supervision, Writing – Review \& editing. \textbf{FC}: Supervision, Writing – Review \& editing. \textbf{SLB}: Resources, Writing – Review \& editing. \textbf{LC}: Funding Acquisition, Resources. \textbf{MG}: Conceptualisation, Methodology, Resources, Supervision, Writing – Review \& editing.

\paragraph{Chapter 4}
\textbf{MDu}: Conceptualization, Investigation, Methodology, Software, Formal analysis, Visualisation, Writing – original draft. \textbf{GP}: Conceptualization, Methodology, Supervision, Writing – Review \& editing. \textbf{MDa}: Investigation, Methodology, Funding Acquisition, Writing – Review \& editing. \textbf{JB}: Investigation, Funding Acquisition, Resources, Writing – Review \& editing. \textbf{EV}: Investigation, Methodology. \textbf{SLB}: Resources, Writing – Review \& editing. \textbf{SFP}: Investigation, Methodology. \textbf{JJ}: Methodology, Resources. \textbf{TJL}: Visualisation, Writing – Review \& editing. \textbf{LC}: Funding Acquisition, Resources. \textbf{MG}: Conceptualisation, Investigation, Methodology, Resources, Supervision, Writing – Review \& editing.


\paragraph{Chapter 5}
\textbf{MDu}: Writing – original draft.

