\addcontentsline{toc}{chapter}{Publications arising}
\begin{center}
\textbf{\large Publications arising}
\end{center}

The following publications were produced as part of this dissertation:
\\

\textbf{Chapter 2}
\\
\textbf{Dunn, M.}, Pedersen, G., Basedow, S.L., Daase, M., Falk-Petersen, S., Bachelot, L., Camus, L. \& Geoffroy, M. (2022). Inverse method applied to autonomous broadband hydroacoustic survey detects higher densities of zooplankton in near-surface aggregations than vessel-based net survey. \textit{Canadian Journal of Fisheries and Aquatic Sciences}.

\textbf{Chapter 3}
\\
\textbf{Dunn, M.}, McGowan-Yallop, C., Pedersen, G., Falk-Petersen, S., Daase, M.,  Last, L., Langbehn, T.J., Fielding, S., Brierly, A., Cotter, F., Basedow, S.L., Camus, L. \& Geoffroy, M. Model-informed classification of broadband acoustic backscatter from zooplankton in an in situ mesocosm. Submitted to \textit{ICES Journal of Marine Sciences - Echosounder to the Cloud Symposium Issue} on August 14th 2023.

\textbf{Chapter 4}
\\
\textbf{Dunn, M.}, Pedersen, G., Daase, M., Berge, J., Venables, E., Basedow, S.L., Falk-Petersen, S., Jensen, J., Langbehn T.J.,  Camus, L. \& Geoffroy, M. Classification of three coinciding species (Atlantic cod, polar cod, and northern shrimp) using broadband hydroacoustics. Submitted to \textit{ICES Journal of Marine Sciences - Echosounder to the Cloud Symposium Issue} on August 29th 2023. 
\\
The work from this thesis has been presented in multiple international conferences and workshops:
\begin{itemize}
\item \textbf{Dunn, M.}, Pedersen, G., Basedow, S.L., Daase, M., Camus, L., Falk-Petersen, S. \& Geoffroy, M. (2021). Autonomous measurements of an undisturbed epipelagic sound scattering layer at high latitudes. \textit{Arctic Science Summit Week (Online)}, Lisbon, Portugal.
\item \textbf{Dunn, M.}, Pedersen, G., Basedow, S.L., Daase, M., Falk-Petersen, S., Bachelot, L., Camus, L. \& Geoffroy, M. (2021). AZKABAN: An ex situ experiment for informing the inverse method \textit{ICES Working Group on Fisheries Acoustics Science and Technology (WGFAST) Meeting (Online)}, Bergen, Norway.
\item \textbf{Dunn, M.}, Pedersen, G., Basedow, S.L., Daase, M., Camus, L., Falk-Petersen, S. \& Geoffroy, M. (2022). Comparison of sampling strategies for epipelagic sound scattering layers at high latitudes. \textit{Ocean Sciences Meeting (Online)}, Hawaii, US.
\item \textbf{Dunn, M.}, Pedersen, G., Basedow, S.L., Daase, M., Camus, L., Falk-Petersen, S. \& Geoffroy, M. (2022). Using an autonomous surface vehicle and hydroacoustics to survey epipelagic organisms at high-latitudes. \textit{ Fourth ICES/PICES Early Career Scientist Conference}, St-John's, Canada.
\item \textbf{Dunn, M.} (2022). Get more from EK80 data. \textit{Kongsberg EK80 Workshop Tromsø}, Tromsø, Norway. 
\item \textbf{Dunn, M.}, McGowan-Yallop, C., Pedersen, G., Falk-Petersen, S., Daase, M.,  Last, L., Langbehn, T.J., Fielding, S., Brierly, A., Cotter, F., Basedow, S.L., Camus, L. \& Geoffroy, M. (2023). Model-informed classification of broadband acoustic backscattering from zooplankton in an \textit{in situ} mesocosm. \textit{ICES Symposium: From echosounders to the cloud}, Portland, ME.
\item \textbf{Dunn, M.}, Pedersen, G., Daase, M., Berge, J., Venables, E., Basedow, S.L., Falk-Petersen, S., Jensen, J., Langbehn, T.J.,  Camus, L. \& Geoffroy, M. (2023). Discrimination of target strength spectra from three coinciding Arctic species (\textit{Boreogadus saida, Gadus morhua, Pandalus borealis}).\textit{Canadian Meterological and Oceanographic Society (CMOS) conference} St-John’s, Canada. (Presented by Geoffroy, M.).
\end{itemize}


In addition to my thesis chapters I have published a peer-reviewed publication, contributed to one conference proceedings, four technical or scientific reports and obtained one research grant:
\begin{itemize}
\item Poncon, Y., et al., [including \textbf{Dunn, M.}] (2023) Bioglider: an integrated glider solution for enhancing environmental knowledge. \textit{OCEANS 2023 Gulf Coast conference}, IEEE Oceanic engineering society, Sep 2023, Biloxi, MS, United States.
\item \textbf{Dunn, M.} \& Zedel, L. (2022). Evaluation of discrete target detection with an acoustic Doppler current profiler. \textit{Limnology and Oceanography: Methods}.
\item ICES [including \textbf{Dunn, M.}] (2022). Working Group of Fisheries Acoustics, Science and Technology (WGFAST).\textit{ ICES Scientific Reports}. 4:54. 93 pp.
\item Ramasco, V., \textbf{Dunn, M.} (2021). Sailbuoy in Antarctica: A survey for the Norwegian Polar Institute. \textit{Akvaplan-niva Report}. 2021 62586.01.
\item ICES [including \textbf{Dunn, M.}] (2020). Working Group on Fisheries Acoustics, Science and Technology (WGFAST). \textit{ICES Scientific Reports}. 2:70. 18 pp.
\item \textbf{Dunn, M.} (2021). Arrested Zooplankton Kept Alive for Broadband Acoustic Net experiment for light reactions (AZKABAN-light). Commissioned by the Research Council of Norway (NOK 60 000-).
\item Niemi, A., et al. [including \textbf{Dunn, M.}] (2020). Data from the BREA-MFP and CBS-MEA research programs describing the Anguniaqvia niqiqyuam Marine Protected Area (ANMPA) ecosystem. \textit{Can. Data Rep. Fish. Aquat. Sci.} 1316: ix + 90 p.
\end{itemize}


